---
title: "Homework 03"
format: gfm
editor: visual
---

# Base R and R Basics

HINT: Remember that you can get help on any function by typing `?`(function name). For instance, `?rnorm` gives help on the `rnorm()` function.

## Creating and naming variables

1.  Create a variable called `x` and use it to store the result of the calculation `(3*(4+2)`.
2.  Calculate the product of `x` (from the above question) times π.
3.  Use the `getwd()` function to show your current working directory. Is that a good working directory, and what program do you think set it that way?

## Vectors

1.  Use the `c()` function to create a vector of numbers.
2.  Use the `c()` function to create a vector of characters.
3.  Use the `:` implicit function to create a vector of integers from 1 to 10.
4.  Explain *why* the following code returns what it does. Also address whether you think this was a good decision on the part of the designers of R?

```{r, warning=FALSE}
v1 <- 1:3
v2 <- c(1:4)
v1 + v2
```

5.  Explain what the following code does. It may be helpful to reference the answer to the previous question:

```{r}
c(1, 5, 9) + 3
```

6.  Remove (delete) every variable in your workspace.

## Graphics

1.  Load the tidyverse package. **NOTE:** Be sure to use the chunk option `message=FALSE` to suppress the messages that tidyverse prints when loaded. These messages are useful in the

```{r, message=FALSE}

```

2.  Recreate the visualization of `body_mass_g` to `flipper_length_mm`, from the penguins data set, that is shown in question 8 of section 2.2.5 of [R4DS](https://r4ds.hadley.nz/data-visualize).

3.  Explain why each aesthetic is mapped at the level that it is (i.e., at the global level, in the `ggplot()` function call, or at the geom level, in the `geom_XXX()` function call). Note: A lot of different options will work, but some options are clearly better than others.
